MG7: Configurable and scalable 16S metagenomics data analysis -- new methods optimized for massive cloud computing

### 2015-09-13 docs/paper/out/paper.tex
set loquat version used to 2.0.0 -- paper
cite records, mention cosas -- paper

\href{https://github.com/ohnosequences/datasets}{Datasets} is a Scala
library developed by the first and last authors to declare datasets and
their locations. \textbf{Data} is represented as type-indexed fields:
Keys are modeled as singleton types, and values correspond to what could
be called a denotation of the key: a value of type \texttt{Location}
tagged with the key type. Then a \textbf{Dataset} is essentially a
collection of data, which are guaranteed statically to be different
through type-level predicates, making use of the value ↔ type
correspondence which can be established through singleton types and
implicits. A dataset location is then just a list of locations formed by
locations of each data member of that dataset.

@@

MG7 uses
\href{https://github.com/ohnosequences/loquat/releases/tag/v?.?.?}{ohnosequences/loquat
?.?.?}.

>>>>

\href{https://github.com/ohnosequences/datasets}{Datasets} is a Scala
library developed by the first and last authors to declare datasets and
their locations. \textbf{Data} is represented as type-indexed fields:
Keys are modeled as singleton types, and values correspond to what could
be called a denotation of the key: a value of type \texttt{Location}
tagged with the key type. Then a \textbf{Dataset} is essentially a
collection of data, which are guaranteed statically to be different
through type-level predicates, making use of the value ↔ type
correspondence which can be established through singleton types and
implicits. A dataset location is then just a list of locations formed by
locations of each data member of that dataset. All this is based on what
could be described as an embedding in Scala of an extensible record
system with concatenation on disjoint labels, in the spirit of
\citep[\citet{harper1991record}]{harper1990extensible}. For that
\emph{Datasets} uses
\href{https://github.com/ohnosequences/cosas/releases/tag/v0.7.0}{ohnosequences/cosas
0.7.0}.

@@

MG7 uses
\href{https://github.com/ohnosequences/loquat/releases/tag/v2.0.0}{ohnosequences/loquat
2.0.0}.
